\documentclass[D:/Latex/Internship/Report/Latex/Report.tex]{subfiles}
\usepackage[utf8]{inputenc}
\PassOptionsToPackage{english, british}{babel}
\usepackage[english, british]{babel}
\usepackage{graphicx}
\usepackage{setspace}		%use \doublespacing
\usepackage{hyperref}
\graphicspath{{Figure/}}
\newcommand\NoIndent[1]{%
  \par\vbox{\parbox[t]{\linewidth}{#1}}%
}

\begin{document}
  \chapter{Design Issues}
  \label{chap:Design Issues}
    \section{Constraint issues}
    \label{sec:Constraint issues}


    \section{Function issues}
    \label{sec:Function issues}
      \begin{itemize}
        \item Supported jpeg format files.
        \item Capture photo or streaming video.
        \item The serial output data is a common connection.
      \end{itemize}


    \section{Realtime issues}
    \label{sec:Realtime issues}
      \begin{itemize}
        \item The system is soft-realtime, but the latency allowed must be smaller than 500ms.
      \end{itemize}

    \section{Concurrent issues}  
    \label{sec:Concurrent issues}
      \begin{itemize}
        \item The system can be active in any environment, but not too hot and humid, e.g the drone system.
        \item Muti-function: The system can capture images, processing and transmit them at the same time.
        \item Because of using Uart output connection, the system can easily connect to another system. 
      \end{itemize}

    \section{Reactive issues}
    \label{sec:Reactive issues}
      \begin{itemize}
        \item Discontinuous interaction: Power on demand.
        \item Response to external non-periodic events: Can start or stop capture images at any time.
      \end{itemize}
\end{document}